Generalised Management Strategy Evaluation: modelling biodiversity and food security

### 2019-01-03 notebook/presentation/GMSE_presentation.Rmd
Add Magnus

>>>>

- Formalisation and study of conflict and cooperation between rational decision-makers
- Compatibile with agent-based modelling<footnote>[Adami et al. (2016) *Phys. Life. Rev.* **19**:1-26](http://dx.doi.org/10.1016/j.plrev.2016.08.015)</footnote>
- Can suggest management strategies<footnote>[Tilman et al. 2016 *Theor. Ecol.*](http://link.springer.com/article/10.1007%2Fs12080-016-0318-8)</footnote> and be used to understand stake-holder actions<footnote>[Kark et al. 2015 *Curr. Opin. Environ. Sustainability* **12**:12-24]()</footnote>
- Conceptual unification

![](payoff_matrix_sm.png)
<center>
*Prisoner's dilemma*
</center>

![Public license<footnote>test</footnote>](US_USSR_nukes_sm.png).

## Game theory for wicked problems

<u>**Large strategy space:**</u>

 - **Asymmetric payoffs** (payoffs affected by stake-holder identity)
 - **Multiple choices**
 - **Multiple players**
 - **Iterated interactions** (strategies affected by interaction history)

## Game theory for wicked problems

<u>**Large strategy space:**</u>

 - **Asymmetric payoffs** (payoffs affected by stake-holder identity)
 - **Multiple choices**
 - **Multiple players**
 - **Iterated interactions** (strategies affected by interaction history)

![](magnus.jpg)
<center>
*Magnus Carlsen*<footnote>[Andreas Kontokanis](https://commons.wikimedia.org/wiki/File:Carlsen_Magnus_(30238051906).jpg)</footnote>
</center>
